---
  title: "count_md"
author: "Daphne Chevalier"
date: "2024-10-23"
output: html_document
---
  
  ```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Packages
```{r}
library(ggplot2)
library(ggpubr)
library(ggsignif)
library(data.table)
library(igraph)
library(scales)
library(vegan)
library(RColorBrewer)
library(lme4)
library(DHARMa)
library(performance)
library(mvabund)
library(emmeans)
library(glmmTMB)
library(dlookr)
library(multcomp)
library(multcompView)
library(stringr)
library(car)
```

## Setup

### Count data download

```{r}
all_pitfall_names <- fread("../raw_data/pitfall_names.csv", header = FALSE)

setnames(all_pitfall_names, "V1", "FullName")

all_pitfall_names <- all_pitfall_names[grep("debris", FullName, invert = TRUE)]
all_pitfall_names <- all_pitfall_names[grep("multiple_insects", FullName, invert = TRUE)]
all_pitfall_names$FullName <- gsub(" ", "_", all_pitfall_names$FullName)
all_pitfall_names[, c("Root","Filename") := tstrsplit(FullName, "\\/+(?!\\S*\\/)", perl = TRUE)]
all_pitfall_names[, c("Root","Phylum","Class","Order","Family","Subfamily","Genus","Species") := tstrsplit(Root, "/")]
all_pitfall_names[, c("StartDate", "Site", "PrescribedTreatment", "Distance") := tstrsplit(Filename, "_", fixed = TRUE, type.convert = TRUE)[1:4]]
all_pitfall_names[, Distance := strtrim(Distance, 2)]
all_pitfall_names[, StartDate := as.Date(StartDate)]
all_pitfall_names[, id := .I]
all_pitfall_names <- all_pitfall_names[StartDate > as.Date("2023-06-21")]

metatable <- fread("../cleaned_data/metadata.csv")
metatable <- metatable[!is.na(Site)]

pitfall_names <- all_pitfall_names[metatable, Treatment := i.Treatment, on=.(Site, StartDate)]
pitfall_names <- pitfall_names[Treatment %in% c("A","C","W")]
pitfall_names$Treatment <- factor(pitfall_names$Treatment, levels=c("C","A","W"), ordered = FALSE)

pitfall_names <- pitfall_names[Class != "unclassified_arthropod"]
```

### Biomass data download
```{r}
biomass_c <- fread("../cleaned_data/biomass.csv")
biomass_c <- biomass_c[, StartDate := as.Date(StartDate)]
setnames(biomass_c, "Near", "0m")
setnames(biomass_c, "Far", "5m")
biomass_c <- melt(setDT(biomass_c[, !c("Total")]), id.vars = c("StartDate","Site", "Treatment"), variable.name = "Distance")
setnames(biomass_c, "value", "Biomass")

first_julian_biomass <- julian(min(biomass_c$StartDate))
biomass_c[, StartDateJulian := as.numeric(julian(StartDate)) - as.numeric(first_julian_biomass)]

# unique(biomass_c[, (as.numeric(julian(StartDate)) - min(as.numeric(julian(StartDate)))) / (max(as.numeric(julian(StartDate))) - min(as.numeric(julian(StartDate))))])
# 
# unique(wide_counts[, (as.numeric(julian(StartDate)) - min(as.numeric(julian(StartDate)))) / (max(as.numeric(julian(StartDate))) - min(as.numeric(julian(StartDate))))])

#biomass_c[,StartDateJulian := scale(StartDateJulian)]
biomass_c

biomass_zeroes <- biomass_c[Biomass == 0]
biomass_zeroes[, Phylum := "Arthropod"]
setnames(biomass_zeroes, "Biomass", "Count")

merge(pitfall_names, biomass_zeroes, all.x = TRUE, all.y = TRUE)

biomass_c$Treatment <- factor(biomass_c$Treatment, levels=c("C","W","A"), ordered = FALSE)

taxa_cols <- c("Class","Order","Family","Subfamily","Genus","Species")

my_comparisons <- list(c("C","W"), c("C","A"), c("W","A"))
```

### Add rows for each nested level
We needed our table to be exhaustive, with a row for every taxonomic group. For example, if we counted x individuals of Species S within Genus G within Family F in a given pitfall trap, we wanted a row for each of these groups.
```{r}
wide_counts <- pitfall_names[, !c("FullName", "Root", "Filename", "PrescribedTreatment", "id")][, .N, by=.(Phylum, Class, Order, Family, Subfamily, Genus, Species, Site, Treatment, Distance, StartDate)]
cols <- c("Phylum", "Class", "Order", "Family", "Subfamily", "Genus", "Species")
f <- function(dt) {
  i <- sum(!is.na(dt[,..cols]))
  if (i > 1) {
    dt <- dt[rep(1L, i)]
    for (j in 2:i) set(dt, i = 1:(j - 1), j = j, NA)
  }
  dt
}
wide_counts <- wide_counts[,f(.SD), 1:nrow(wide_counts)][,nrow := NULL][
  ,.(N = sum(N)), Phylum:StartDate
]

setnames(wide_counts, old = "N", new = "Count")
```

### Add Julian date and order treatments
```{r}
first_julian <- julian(min(wide_counts$StartDate))
wide_counts[, StartDateJulian := as.numeric(julian(StartDate)) - as.numeric(first_julian)]

#wide_counts[,StartDateJulian := scale(StartDateJulian)]
wide_counts

wide_counts$Treatment <- factor(wide_counts$Treatment, levels=c("C","W","A"), ordered = FALSE)

```

## Size calculation

```{r}
capture_size <- wide_counts[Phylum == "Arthropoda" & is.na(Class)]
capture_size <- capture_size[biomass_c, on = .(StartDate, Site, Treatment, Distance)]
capture_size <- capture_size[Phylum == "Arthropoda"]

capture_size[, Size := Biomass/Count * 1000]

capture_size$Treatment <- factor(capture_size$Treatment, levels=c("C","W","A"), ordered = FALSE)
```

## Boxplots
### Old
```{r}
# Count
pdf("../plots/count_box_all.pdf", w = 15, h = 9)
ggplot(capture_size, aes(Treatment,Count)) +
  geom_boxplot(outlier.shape = NA) +
  theme(axis.text=element_text(size=24),
        axis.title=element_text(size=24,face="bold"),
        title = element_text(size=25, face = "bold")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(title = "More arthropods captured under white light than in darkness") +
  stat_compare_means(method = "wilcox.test", comparisons = my_comparisons, size = 8)

# Size
pdf("../plots/size_box_all.pdf", w = 15, h = 9)
ggplot(capture_size, aes(Treatment,Size)) +
  geom_boxplot(outlier.shape = NA) +
  theme(axis.text=element_text(size=22),
        axis.title=element_text(size=22,face="bold"),
        title = element_text(size=24, face = "bold")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(title = "Larger arthropods (on average) captured under lit conditions") +
  ylab("Size (mg/arthropod)") +
  theme(plot.title = element_text(hjust = 0.5)) +
  stat_compare_means(method = "wilcox.test", comparisons = my_comparisons, size = 8)
dev.off()
```

### Setup for faceted biomass/count/size boxplots
```{r}
bsc <- melt(capture_size[, c("Site", "Treatment", "Distance", "StartDateJulian", "Biomass", "Count", "Size")], 
            id.vars = c("Site", "Treatment", "Distance", "StartDateJulian"), variable.name = "Measure")

box_labels <- c('Biomass' = 'Arthropod biomass (g)', 'Count' = 'Total arthropod count', 'Size' = 'Arthropod biomass/count (mg)')
```

### Biomass, count, and size
```{r}
pdf("../plots/bsc_box_all.pdf", w = 15, h = 9)
ggplot(bsc, aes(Treatment, value)) +
  geom_boxplot() +
  geom_point(alpha = 0.3, position = position_jitter(seed = 1, width = 0.2)) +
  theme(panel.grid = element_blank()) +
  labs(y="") +
  theme(axis.text=element_text(size=16),
        axis.title=element_text(size=22,face="bold"),
        title = element_text(size=22, face = "bold"),
        strip.text = element_text(size = 13)) +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_y_continuous(trans='log10') +
  scale_x_discrete(labels = c("No light", "White", "Amber")) +
  #stat_compare_means(method = "wilcox.test", comparisons = my_comparisons) +
  facet_grid(rows = vars(Measure), scales = "free_y", labeller = labeller(Measure = box_labels))
dev.off()
```

### Count and size
```{r}
pdf("../plots/countsize_box_all.pdf", w = 15, h = 9)
ggplot(bsc[Measure == "Count" | Measure == "Size"], aes(Treatment, value)) +
  geom_boxplot() +
  geom_point(alpha = 0.3, position = position_jitter(seed = 1, width = 0.2)) +
  theme(panel.grid = element_blank()) +
  labs(y="") +
  theme(axis.text=element_text(size=16),
        axis.title=element_text(size=22,face="bold"),
        title = element_text(size=22, face = "bold"),
        strip.text = element_text(size = 13)) +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_y_continuous(trans='log10') +
  scale_x_discrete(labels = c("No light", "White", "Amber")) +
  #stat_compare_means(method = "wilcox.test", comparisons = my_comparisons) +
  facet_grid(rows = vars(Measure), scales = "free_y", labeller = labeller(Measure = box_labels))
dev.off()
```

### Biomass
```{r}
pdf("../plots/biomass_box_all.pdf", w = 15, h = 9)
ggplot(bsc[Measure == "Biomass"], aes(Treatment, value)) +
  geom_boxplot() +
  #geom_point(alpha = 0.3, position = position_jitter(seed = 1, width = 0.2)) +
  theme(panel.grid = element_blank()) +
  labs(y = "Biomass (grams)", title = "Biomass captured across treatments") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(axis.text=element_text(size=16),
        axis.title=element_text(size=22,face="bold"),
        title = element_text(size=22, face = "bold"),
        strip.text = element_text(size = 13)) +
  ylim(0, 15) +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_x_discrete(labels = c("No light", "White", "Amber"))
dev.off()
```

### Count
```{r}
pdf("../plots/count_box_all.pdf", w = 15, h = 9)
ggplot(capture_size, aes(Treatment,Count)) +
  geom_boxplot(outlier.shape = NA) +
  theme(axis.text=element_text(size=24),
        axis.title=element_text(size=24,face="bold"),
        title = element_text(size=25, face = "bold")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(title = "More arthropods captured under white light than in darkness") +
  stat_compare_means(method = "wilcox.test", comparisons = my_comparisons, size = 8)
dev.off()
```

### Classes
```{r}
pdf("../plots/classes.pdf", w = 15, h = 9)
ggplot(wide_counts[!is.na(Class) & is.na(Order), sum(Count), by=Class], aes(x = Class, fill = Class, y = V1)) +
  geom_col() +
  scale_fill_brewer(palette = "YlGnBu") +
  theme(axis.text=element_text(size=24),
        axis.title=element_text(size=24,face="bold"),
        title = element_text(size=25, face = "bold")) +
  theme(plot.title = element_text(hjust = 0.5),
        legend.position="none") +
  scale_y_continuous(trans='log10') +
  labs(title = "Number of arthropods captured across classes") +
  ylab("Count (log scale)")
dev.off()
```
### Insect orders
```{r}
pdf("../plots/orders.pdf", w = 15, h = 9)
ggplot(wide_counts[Class == "Insecta" & !is.na(Order) & is.na(Family), sum(Count), by=Order], aes(x = Order, fill = Order, y = V1)) +
  geom_col() +
  scale_fill_brewer(palette = "YlGnBu") +
  theme(axis.text=element_text(size=24),
        axis.title=element_text(size=24,face="bold"),
        title = element_text(size=25, face = "bold"),
        axis.text.x = element_text(angle = 45, hjust=1)) +
  theme(plot.title = element_text(hjust = 0.5),
        legend.position="none") +
  scale_y_continuous(trans='log10') +
  labs(title = "Number of insects captured across orders") +
  ylab("Count (log scale)")
dev.off()
```
## Functions for formatting model outputs
```{r}
summaries_file <- "../cleaned_data/summaries.csv"

if (file.exists(summaries_file)) {
  file.remove(summaries_file)
}

write_summary <- function(summary_obj) {
  summary_table <- data.table(names(summary_obj[,1]),
             sapply(as.data.table(summary_obj), function(N) prettyNum(signif(N, digits = 3))))
  setnames(summary_table, names(summary_table), append(deparse(substitute(summary_obj)),colnames(summary_obj)))
fwrite(summary_table, file = "../cleaned_data/summaries.csv", append = TRUE,  col.names = TRUE)
}

#anova_obj <- "clear"
write_anova <- function(anova_obj) {
  anova_table <- data.table(rownames(anova_obj),
             sapply(as.data.table(anova_obj), function(N) prettyNum(signif(N, digits = 3))))
  setnames(anova_table, names(anova_table), append(deparse(substitute(anova_obj)),names(anova_obj)))
fwrite(anova_table, file = "../cleaned_data/summaries.csv", append = TRUE,  col.names = TRUE)
}
```

## Simple biomass model
```{r}
#lme_biomass <- glmmTMB(Biomass ~ Treatment * Distance + StartDateJulian + (1|Site) + (1|Site:Distance),
lme_biomass <- glmmTMB(sqrt(Biomass) ~ Treatment * Distance,
                       data = biomass_c)
plot(simulateResiduals(lme_biomass))
summary(lme_biomass)
emmgrid <- emmeans(lme_biomass, specs=pairwise~Treatment*Distance, type="response")
emmgrid$contrasts
emmeans(lme_biomass, list(pairwise ~ Treatment), adjust = "tukey")

write_summary(coef(summary(lme_biomass))$cond)
write_anova(Anova(lme_biomass))
```


## Pooled count model, only treatment
```{r}
lme_count_lim <- glmmTMB(Count ~ Treatment,
                         data = wide_counts[Phylum == "Arthropoda" & is.na(Class)],
                         family = "nbinom2")
plot(simulateResiduals(lme_count_lim))
#r2_nakagawa(lme_count)
summary(lme_count_lim)
emmeans(lme_count_lim, list(pairwise ~ Treatment), adjust = "tukey")
```

## Pooled count model
```{r}
lme_count <- glmmTMB(Count ~ Treatment * Distance + StartDateJulian + (1|Site) + (1|Site:Distance),
                     data = wide_counts[Phylum == "Arthropoda" & is.na(Class)],
                     family = "nbinom2")
plot(simulateResiduals(lme_count))

#r2_nakagawa(lme_count)
summary(lme_count)
emmeans(lme_count, list(pairwise ~ Treatment), adjust = "tukey")

write_summary(coef(summary(lme_count))$cond)
write_anova(Anova(lme_count))
```

## Pooled size model
```{r}
lme_size <- lmer(sqrt(Size) ~ Treatment * Distance + StartDateJulian + (1|Site) + (1|Site:Distance), data = capture_size)
summary(lme_size)
plot(simulateResiduals(lme_size))
emmeans(lme_size, list(pairwise ~ Treatment), adjust = "tukey")
anova(lme_size)
r2_nakagawa(lme_size)

write_summary(coef(summary(lme_size))$cond)
write_anova(Anova(lme_size))
```

# Taxon-specific models
## Classes
Add zero rows.
```{r}
zero_classes <- wide_counts[!is.na(Class) & is.na(Order) & !is.na(Treatment), .SD, .SDcols = c("Class", "Site", "Treatment", "Distance", "StartDateJulian", "Count")]

zero_classes_cj <- zero_classes[
  CJ(Class = Class,
     Site = Site,
     Distance = Distance,
     StartDateJulian = StartDateJulian,
     unique = TRUE), 
  on = .(Class, Site, Distance, StartDateJulian)
]
# we have 2 kinds of NA row now:
# the kind that has a corresponding pitfall trap (value in metadata)
# the kind that doesn't

View(zero_classes_cj)

#zero_classes_cj[, .N, by=Treatment]

metatable[, StartDateJulian := as.numeric(julian(StartDate)) - as.numeric(first_julian)]

View(zero_classes_cj[metatable, on=.(Site, StartDateJulian)])

#zero_classes_cj[metatable, on=.(Site, StartDateJulian)][, .N, by=Treatment]
#, Treatment := i.Treatment][is.na(Treatment)])

View(zero_classes_cj[metatable, on=.(Site, StartDateJulian), Treatment := i.Treatment])

zero_classes_cj <- zero_classes_cj[metatable, on=.(Site, StartDateJulian), Treatment := i.Treatment][Treatment %in% c("A", "C", "W")]

#View(zero_classes_cj[zero_classes, on=.(Site, StartDateJulian), Treatment2 := i.Treatment][, .(Site, StartDateJulian, Treatment = fcoalesce(Treatment2, as.factor(Treatment)))])

#rbind(zero_classes, zero_classes_cj[!zero_classes, on=.(Site, StartDateJulian)])

setnafill(zero_classes_cj, fill = 0, cols=c("Count"))
```





Select most-frequently-occurring taxa.
```{r}
classes <- zero_classes_cj[, sum(Count), by=Class][zero_classes_cj, on=c("Class")][V1>0.03*sum(unique(V1))][,.SD, .SDcols = !c('V1')]
factor_cols <- c("Class", "Distance", "Site")
classes[, (factor_cols) := lapply(.SD, factor, ordered = FALSE), .SDcols = factor_cols]
```

Model.
```{r}
lme_class_1 <- glmmTMB(Count ~ Class + Treatment : Class + Treatment * Distance + StartDateJulian + (1|Site) + (1|Site:Distance),
                       data = classes,
                       #ziformula= ~1,
                       family="nbinom2")
plot(simulateResiduals(lme_class_1))
testZeroInflation(simulateResiduals(lme_class_1))
testDispersion(simulateResiduals(lme_class_1), type = "DHARMa")
testOutliers(simulateResiduals(lme_class_1))

lme_class <- glmmTMB(Count ~ Class * Treatment * Distance + StartDateJulian + (1|Site) + (1|Site:Distance),
                     data = classes,
                     #ziformula= ~1,
                     family="nbinom2")
plot(simulateResiduals(lme_class))
testZeroInflation(simulateResiduals(lme_class))
testDispersion(simulateResiduals(lme_class), type = "DHARMa")
testOutliers(simulateResiduals(lme_class))

```

Interactions.
```{r}
summary(lme_class)
Anova(lme_class)

pdf("../plots/classes_emmips", w = 5, h = 3)
emmip(lme_class, Class ~ Distance | Treatment)
dev.off()



```

Plot.
```{r}
emmeans(lme_class, ~Treatment * Class, type="response")
plot(emmeans(lme_class, ~Treatment | Class, type="response"), comparisons = TRUE)
pairs(emmeans(lme_class, ~Class * Treatment | Distance, type="response"), simple = "each", adjust = "holm")
pairs(emmeans(lme_class, ~Class * Distance | Treatment, type="response"), simple = "each", adjust = "holm")
summary(lme_class)
```



Per trap.
```{r}
# we want a stacked bar graph

pitfall_classes <- zero_classes_cj[, .(Traps = .N, Number = sum(Count), PerTrap = mean(Count), SD = sd(Count)/.N), by=.(Class, Distance, Treatment)]

pitfall_classes[, sum(Number), by=Class]

pdf("../plots/classes_treatments", w = 15, h = 9)
ggplot(pitfall_classes, aes(x = Class, y = PerTrap, group = Treatment, fill = Treatment)) +
  geom_col(position = "dodge") +
  geom_errorbar(aes(ymin = PerTrap-SD, ymax = PerTrap+SD), position = "dodge") +
  scale_fill_manual(values = c("C" = "black",
                               "A" = "orange",
                               "W" = "grey")) +
  theme(panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text.x = element_text(angle = 45, hjust=1),
    axis.text=element_text(size=20),
    plot.title = element_text(hjust = 0.5),
    axis.title=element_text(size=24,face="bold"),
    title = element_text(size=24, face = "bold"),
    strip.text = element_text(size = 18),
    axis.ticks = element_blank(),
    legend.text = element_text(size = 18)) +
    ylab("Average number of arthropods per trap") +
  labs(title = "Number of arthropods captured across classes") +
  facet_grid(rows = vars(Distance), scales = "free_y")
dev.off()
```









## Orders
Add zero rows.
```{r}
zero_orders <- wide_counts[!is.na(Order) & is.na(Family) & !is.na(Treatment), .SD, .SDcols = c("Order", "Site", "Treatment", "Distance", "StartDateJulian", "Count")]
zero_orders_cj <- zero_orders[
  CJ(Order = Order,
     Site = Site,
     Distance = Distance,
     StartDateJulian = StartDateJulian,
     unique = TRUE), 
  on = .(Order, Site, Distance, StartDateJulian)
]
metatable[, StartDateJulian := as.numeric(julian(StartDate)) - as.numeric(first_julian)]
zero_orders_cj <- zero_orders_cj[metatable, on=.(Site, StartDateJulian), Treatment := i.Treatment][Treatment %in% c("A", "C", "W")]
setnafill(zero_orders_cj, fill = 0, cols=c("Count"))

# zero_orders <- wide_counts[!is.na(Order) & is.na(Family) & !is.na(Treatment), .SD, .SDcols = c("Order", "Site", "Treatment", "Distance", "StartDateJulian", "Count")]
# 
# zero_orders <- zero_orders[
#   CJ(Order = Order,
#      Site = Site,
#      Distance = Distance,
#      StartDateJulian = StartDateJulian,
#      unique = TRUE), 
#   on = .(Order, Site, Distance, StartDateJulian)
# ]
# 
# zero_orders[, .N, by=.(Site, StartDateJulian, Order, Distance)]
# 
# setnafill(zero_orders, fill = 0, cols=c("Count"))
```



Select most-frequently-occurring taxa.
```{r}
orders <- zero_orders_cj[, sum(Count), by=Order][zero_orders_cj, on=c("Order")][V1>0.03*sum(unique(V1))][,.SD, .SDcols = !c('V1')]
factor_cols <- c("Order", "Distance", "Site")
orders[, (factor_cols) := lapply(.SD, factor, ordered = FALSE), .SDcols = factor_cols]
```

Model.
```{r}
lme_order_1 <- glmmTMB(Count ~ Order + Treatment : Order + Treatment * Distance + StartDateJulian + (1|Site) + (1|Site:Distance),
                       data = orders,
                       #ziformula= ~1,
                       family="nbinom2")
plot(simulateResiduals(lme_order_1))
testZeroInflation(simulateResiduals(lme_order_1))
testDispersion(simulateResiduals(lme_order_1), type = "DHARMa")
testOutliers(simulateResiduals(lme_order_1))

lme_order <- glmmTMB(Count ~ Order * Treatment * Distance + StartDateJulian + (1|Site) + (1|Site:Distance),
                     data = orders,
                     #ziformula= ~1,
                     family="nbinom2")
plot(simulateResiduals(lme_order))
testZeroInflation(simulateResiduals(lme_order))
testDispersion(simulateResiduals(lme_order), type = "DHARMa")
testOutliers(simulateResiduals(lme_order))
```

Interaction analysis.
```{r}
pdf("../plots/orders_emmips", w = 5, h = 3)
emmip(lme_order, Order ~ Distance | Treatment)
dev.off()



write_table(coef(summary(lme_order))$cond)
write_anova(Anova(lme_order))

```

Plot.
```{r}
emmeans(lme_order, ~Treatment * Order, type="response")
plot(emmeans(lme_order, ~Treatment | Order, type="response"), comparisons = TRUE)
pairs(emmeans(lme_order, ~Order * Treatment, type="response"), simple = "each", adjust = "holm")
pairs(emmeans(lme_order, ~Order * Distance | Treatment, type="response"), simple = "each", adjust = "holm")
```



Per trap.
```{r}
pitfall_orders <- zero_orders_cj[, .(Traps = .N, Number = sum(Count), PerTrap = sum(Count)/.N), by=.(Order, Distance, Treatment)]

pitfall_orders[, sum(Number), by=Order]

pdf("../plots/orders_treatments", w = 15, h = 9)
ggplot(pitfall_orders, aes(x = Order, y = PerTrap, group = Treatment, fill = Treatment)) +
  geom_col(position = "dodge") +
  scale_fill_manual(values = c("C" = "black",
                               "A" = "orange",
                               "W" = "grey")) +
  theme(panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text.x = element_text(angle = 45, hjust=1),
    axis.text=element_text(size=20),
    plot.title = element_text(hjust = 0.5),
    axis.title=element_text(size=24,face="bold"),
    title = element_text(size=24, face = "bold"),
    strip.text = element_text(size = 18),
    axis.ticks = element_blank(),
    legend.text = element_text(size = 18)) +
  ylab("Average number of arthropods per trap") +
  labs(title = "Number of arthropods captured across orders") +
  facet_grid(rows = vars(Distance), scales = "free_y")
dev.off()
```








## Families
Get the families, add zero rows.
```{r}
zero_fams <- wide_counts[!is.na(Family) & is.na(Subfamily) & !is.na(Treatment), .SD, .SDcols = c("Family", "Site", "Treatment", "Distance", "StartDateJulian", "Count")]
zero_fams_cj <- zero_fams[
  CJ(Family = Family,
     Site = Site,
     Distance = Distance,
     StartDateJulian = StartDateJulian,
     unique = TRUE), 
  on = .(Family, Site, Distance, StartDateJulian)
]
metatable[, StartDateJulian := as.numeric(julian(StartDate)) - as.numeric(first_julian)]
zero_fams_cj <- zero_fams_cj[metatable, on=.(Site, StartDateJulian), Treatment := i.Treatment][Treatment %in% c("A", "C", "W")]
setnafill(zero_fams_cj, fill = 0, cols=c("Count"))

```

Filter on frequency.
```{r}
families_freq <- zero_fams_cj[, sum(Count), by=Family][zero_fams_cj, on=c("Family")][V1>0.03*sum(unique(V1))][,.SD, .SDcols = !c('V1')]
factor_cols <- c("Family", "Distance", "Site")   
families_freq[, (factor_cols) := lapply(.SD, factor, ordered = FALSE), .SDcols = factor_cols]
families_freq[Count != 0, sum(Count), by=Family]
```

Model.
```{r}
lme_fam_1 <- glmmTMB(Count ~ Family + Treatment : Family + Treatment * Distance + StartDateJulian + (1|Site) + (1|Site:Distance),
                     data = families_freq,
                     #ziformula=~1,
                     family=nbinom2)
plot(simulateResiduals(lme_fam_1))
testZeroInflation(simulateResiduals(lme_fam_1))
testDispersion(simulateResiduals(lme_fam_1), type = "DHARMa")
testOutliers(simulateResiduals(lme_fam_1))

lme_fam <- glmmTMB(Count ~ Family * Treatment * Distance + StartDateJulian + (1|Site) + (1|Site:Distance),
                   data = families_freq,
                   #ziformula=~1,
                   family=nbinom2)
summary(lme_fam)
plot(simulateResiduals(lme_fam))
testZeroInflation(simulateResiduals(lme_fam))
testDispersion(simulateResiduals(lme_fam), type = "DHARMa")
testOutliers(simulateResiduals(lme_fam))

pdf("../plots/fams_emmips", w = 5, h = 3)
emmip(lme_fam, Family ~ Distance | Treatment)
dev.off()
pairs(emmeans(lme_fam, ~Family * Distance | Treatment, type="response"), simple = "each", adjust = "holm")
pairs(emmeans(lme_fam, ~Family * Treatment, type="response"), simple = "each", adjust = "holm")



```

Plot.
```{r}
plot(emmeans(lme_fam, ~Treatment | Family, type="response"), comparisons = TRUE)
pairs(emmeans(lme_fam, ~Family * Treatment, type="response"), simple = "each", adjust = "holm")


fam_emms <- emmeans(lme_fam, ~ Treatment | Family)
fam_cons <- contrast(fam_emms, "revpairwise")
fam_contrasts <- as.data.table(summary(fam_cons, type = "response", simple = "each", adjust = "holm"))
fam_contrasts[, Significant := (p.value < 0.05)]

# geom_text(aes(y = text_location,label = value), vjust = 0.0, size = 5)

pdf("../plots/ratios_fam_new.pdf", w = 15, h = 9)
ggplot(data = fam_contrasts[contrast == "W / C" | contrast == "A / C"], aes(x = contrast, y = ratio, fill = contrast)) +
  geom_col() +
  geom_errorbar(aes(ymin = ratio-SE, ymax = ratio+SE)) +
  geom_text(aes(label = ifelse(Significant, "*", ""), group = contrast, y = ratio + (-1 + 2 * as.numeric(ratio > 1)) * SE),
  size = 26/ .pt) +
  facet_grid(cols = vars(Family)) +
  theme(panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text.x = element_blank(),
    axis.text=element_text(size=24),
    axis.title=element_text(size=24,face="bold"),
    title = element_text(size=22, face = "bold",hjust = 0.5),
    strip.text = element_text(size = 18),
    axis.ticks = element_blank(),
    legend.text = element_text(size = 18)) +
  scale_y_continuous(trans= "log10") +
  labs(title = "Ratio between estimated count under lit and unlit conditions, across families") +
  scale_fill_manual(values = c("W / C" = "grey", "A / C" = "#E69F00"))
dev.off()

Anova(lme_fam)

as.data.table(emmeans(lme_fam, ~ Treatment * Family, type = "response", adjust = "holm"))

emmeans(lme_fam, pairwise~Treatment, adjust = "tukey")

fam_resp <- as.data.table(emmeans(lme_fam, ~ Treatment * Family, type = "response", adjust = "holm"))
pdf("../plots/ratios_fam_new.pdf", w = 15, h = 9)
ggplot(data = fam_resp, aes(x = Family, y = response, fill = Treatment)) +
  geom_col(position = "dodge") +
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL), position = "dodge") +
  #geom_text(aes(label = ifelse(Significant, "*", ""), group = contrast, y = ratio + (-1 + 2 * as.numeric(ratio > 1)) * SE),
  #size = 26/ .pt) +
  #facet_grid(cols = vars(Family)) +
  theme(panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text=element_text(size=24),
    axis.text.x = element_text(angle = 45, hjust=1),
    axis.title=element_text(size=24,face="bold"),
    title = element_text(size=22, face = "bold",hjust = 0.5),
    strip.text = element_text(size = 18),
    axis.ticks = element_blank(),
    legend.text = element_text(size = 18)) +
  scale_y_continuous(trans= "log10") +
  labs(title = "Response") +
  scale_fill_manual(values = c("W" = "grey", "A" = "#E69F00", "C" = "black"))
dev.off()



```

Per trap.
```{r}
pitfall_families <- zero_fams_cj[, .(Traps = .N, Number = sum(Count), PerTrap = sum(Count)/.N), by=.(Family, Distance, Treatment)]

pitfall_families[, sum(Number), by=Family]

#SD = sd(Count)/.N)

pdf("../plots/families_treatments", w = 15, h = 9)
ggplot(pitfall_families, aes(x = Family, y = PerTrap, group = Treatment, fill = Treatment)) +
  geom_col(position = "dodge") +
  scale_fill_manual(values = c("C" = "black",
                               "A" = "orange",
                               "W" = "grey")) +
  theme(panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text.x = element_text(angle = 45, hjust=1),
    axis.text=element_text(size=20),
    axis.title=element_text(size=24,face="bold"),
    title = element_text(size=24, face = "bold"),
    strip.text = element_text(size = 18),
    axis.ticks = element_blank(),
    legend.text = element_text(size = 18)) +
    ylab("Average number of arthropods per trap") +
  labs(title = "Number of arthropods captured across families") +
  facet_grid(rows = vars(Distance), scales = "free_y")
dev.off()

```
```{r}
lme_fam_summary <- summary(emmeans(lme_fam, ~Treatment : Family, type="response"), 
                             comparisons = TRUE)

lme_fam_means <- emmeans(object = lme_fam,
                           specs = ~ Treatment : Family,
                           type = "response")

lme_fam_cld <- cld(object = lme_fam_means,
                     adjust = "Tukey",
                     Letters = letters,
                     alpha = 0.05)
lme_fam_cld

#geom_text(aes(label = ifelse(Significant, "*", ""), group = contrast, y = ratio + (-1 + 2 * as.numeric(ratio > 1)) * SE),

ggplot(pitfall_families[Family %in% families_freq$Family], aes(x = Family, y = PerTrap, group = Treatment, fill = Treatment)) +
  geom_col(position = "dodge") +
  scale_fill_manual(values = c("C" = "black",
                               "A" = "orange",
                               "W" = "grey")) +
  theme(panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text.x = element_text(angle = 45, hjust=1),
    axis.text=element_text(size=20),
    axis.title=element_text(size=24,face="bold"),
    title = element_text(size=24, face = "bold"),
    strip.text = element_text(size = 18),
    axis.ticks = element_blank(),
    legend.text = element_text(size = 18)) +
    ylab("Average number of arthropods per trap") +
  labs(title = "Number of arthropods captured across families") +
  facet_grid(rows = vars(Distance))
```


## Subfamilies
Get the subfamilies, add zero rows.
```{r}
zero_subfams <- wide_counts[!is.na(Subfamily) & is.na(Genus) & !is.na(Treatment), .SD, .SDcols = c("Subfamily", "Site", "Treatment", "Distance", "StartDateJulian", "Count")]
zero_subfams_cj <- zero_subfams[
  CJ(Subfamily = Subfamily,
     Site = Site,
     Distance = Distance,
     StartDateJulian = StartDateJulian,
     unique = TRUE), 
  on = .(Subfamily, Site, Distance, StartDateJulian)
]
metatable[, StartDateJulian := as.numeric(julian(StartDate)) - as.numeric(first_julian)]
zero_subfams_cj <- zero_subfams_cj[metatable, on=.(Site, StartDateJulian), Treatment := i.Treatment][Treatment %in% c("A", "C", "W")]
setnafill(zero_subfams_cj, fill = 0, cols=c("Count"))
```

Filter for frequency.
```{r}
subfamilies_freq <- zero_subfams_cj[zero_subfams_cj[, sum(Count), by=Subfamily][V1>0.01*sum(unique(V1))], on=c("Subfamily")]
subfamilies_freq[Count != 0, sum(Count), by=Subfamily]
```

Model.
```{r}
lme_sub <- glmmTMB(Count ~ Subfamily * Treatment * Distance + StartDateJulian + (1|Site) + (1|Site:Distance),
                   data = subfamilies_freq,
                   #ziformula=~1,
                   family=nbinom2)
plot(simulateResiduals(lme_sub))
testZeroInflation(simulateResiduals(lme_sub))
testDispersion(simulateResiduals(lme_sub), type = "DHARMa")
testOutliers(simulateResiduals(lme_sub))
```

Plot.
```{r}
emmeans(lme_sub, ~Treatment * Subfamily, type="response")
pairs(emmeans(lme_sub, ~Subfamily * Treatment, type="response"), simple = "each", adjust = "holm")

plot(emmeans(lme_sub, ~Treatment | Subfamily, type="response"), comparisons = TRUE)
```


## Genera
Get the genera, add zero rows.
```{r}
zero_genera <- wide_counts[!is.na(Genus) & is.na(Species) & !is.na(Treatment), .SD, .SDcols = c("Genus", "Site", "Treatment", "Distance", "StartDateJulian", "Count")]
zero_genera_cj <- zero_genera[
  CJ(Genus = Genus,
     Site = Site,
     Distance = Distance,
     StartDateJulian = StartDateJulian,
     unique = TRUE), 
  on = .(Genus, Site, Distance, StartDateJulian)
]
zero_genera_cj <- zero_genera_cj[metatable, on=.(Site, StartDateJulian), Treatment := i.Treatment][Treatment %in% c("A", "C", "W")]
setnafill(zero_genera_cj, fill = 0, cols=c("Count"))
```

Filter for frequency.
```{r}
genera_freq <- zero_genera_cj[zero_genera_cj[, sum(Count), by=Genus][V1>0.03*sum(unique(V1))], on=c("Genus")]
```

Model.
```{r}
lme_gen <- glmmTMB(Count ~ Genus * Treatment * Distance + StartDateJulian + (1|Site) + (1|Site:Distance),
                     data = genera_freq,
                     ziformula=~1,
                     family=nbinom2)
summary(lme_gen)
plot(simulateResiduals(lme_gen))
testZeroInflation(simulateResiduals(lme_gen))
testDispersion(simulateResiduals(lme_gen), type = "DHARMa")
testOutliers(simulateResiduals(lme_gen))
```

Plot.
```{r}
emmeans(lme_gen, ~Treatment * Genus, type="response")
pairs(emmeans(lme_gen, ~Genus * Treatment, type="response"), simple = "each", adjust = "holm")
pairs(emmeans(lme_gen, ~Genus * Treatment, type="response"), simple = "each", adjust = "holm")
plot(emmeans(lme_gen, ~Treatment | Genus, type="response"), comparisons = TRUE)
```




## species
Get the species, add zero rows.
```{r}
zero_species <- wide_counts[!is.na(Species) & !is.na(Treatment), .SD, .SDcols = c("Species", "Site", "Treatment", "Distance", "StartDateJulian", "Count")]
zero_species_cj <- zero_species[
  CJ(Species = Species,
     Site = Site,
     Distance = Distance,
     StartDateJulian = StartDateJulian,
     unique = TRUE), 
  on = .(Species, Site, Distance, StartDateJulian)
]
zero_species_cj <- zero_species_cj[metatable, on=.(Site, StartDateJulian), Treatment := i.Treatment][Treatment %in% c("A", "C", "W")]
setnafill(zero_species_cj, fill = 0, cols=c("Count"))
```

Filter for frequency.
```{r}
species_freq <- zero_species_cj[zero_species_cj[, sum(Count), by=Species][V1>0.03*sum(unique(V1))], on=c("Species")]
```

Model.
```{r}
lme_spec <- glmmTMB(Count ~ Species * Treatment * Distance + StartDateJulian + (1|Site) + (1|Site:Distance),
                      data = species_freq,
                      ziformula=~1,
                      family=nbinom2)
summary(lme_spec)
plot(simulateResiduals(lme_spec))
testZeroInflation(simulateResiduals(lme_spec))
testDispersion(simulateResiduals(lme_spec), type = "DHARMa")
testOutliers(simulateResiduals(lme_spec))
```

Plot.
```{r}
emmeans(lme_spec, ~Treatment * Species, type="response")
pairs(emmeans(lme_spec, ~Species * Treatment, type="response"), simple = "each", adjust = "holm")

plot(emmeans(lme_spec, ~Treatment | Species, type="response"), comparisons = TRUE)
```



## Plotting emmeans
```{r}
lme_fam_1_summary <- summary(emmeans(lme_fam_1, ~Treatment : Family, type="response"), 
                             comparisons = TRUE)

lme_fam_1_means <- emmeans(object = lme_fam_1,
                           specs = ~ Treatment : Family,
                           type = "response")

lme_fam_1_cld <- cld(object = lme_fam_1_means,
                     adjust = "Tukey",
                     Letters = letters,
                     alpha = 0.05)
lme_fam_1_cld
```


## Including Plots

You can also embed plots, for example:
  
  ```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
